Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-03-20 ms.tex
started describing absolute zero point procedure

\subsection{Zero-Point}
\label{sec:zp}
Although we wish to isolate and model thermal emission from Galactic dust, the
\PLANCK~maps contain additional components on large angular scales. At each 
frequency, there can exist an overall, constant offset that must be subtracted 
to set the zero level of Galactic dust. Additionally, faint residuals of the 
Solar dipole remain at low frequencies. At 353 GHz, 545 GHz, 857 GHz, we have 
adopted the zero-point offsets of \cite{planckdust} Table 1, which were derived
 by correlating \PLANCK~857 GHz versus H\,\textsc{i} at low column density, and
then by correlating the other \PLANCK~channels against the corrected 857 GHz 
map. We have not altered the \verb|i100| zero-point in any way. We have also 
removed the Solar dipole residual according to \cite{planckdust}, by 
subtracting a dipole pattern oriented toward 
$(l, b) = (263.99^{\circ}, 48.26^{\circ})$ and scaled according to their 
Table 1.

>>>>

\subsection{Zero-Point}
\label{sec:zp}

% for quantitative assessment of the zero-point difference due to
% flattening of 857 GHz vs. HI, see 
% ~/Desktop/dust/planck_hi/piecewise.pdf (on my Mac)

% -> at low HI, slope decreases by a factor of 1.88
%    the resulting difference in 857 GHz zero points is 0.373 MJy/sr

Although we wish to isolate and model thermal emission from Galactic dust, the
\PLANCK~maps contain additional components on large angular scales. At each 
frequency, there can exist an overall, constant offset that must be subtracted 
to set the zero level of Galactic dust. Additionally, faint residuals of the 
Solar dipole remain at low frequencies. We will address these issues by
separately solving two sub-problems: the relative offsets and low order
corrections derived by correlating the \PLANCK~bands against one another,
and second the absolute zero-level offset.
%this last sentence needs lots of work

\subsubsection{Absolute Zero Level}
In \cite{planckdust}, the absolute zero level of infrared thermal dust emission
is set by requiring that \PLANCK~infrared emission tends to zero when 
H\,\textsc{i} is zero, assuming a linear correlation between these two 
measurements at low column density. However, this approach is somewhat
unsatisfying in that there appear to be different slopes of 857 GHz versus
H\,\textsc{i} for different ranges of H\,\textsc{i}. In particular, 
\PLANCK~857 GHz appears to ``flatten out'' at very low H\,\textsc{i}. More 
quantitavely, we have found using the LAB H\,\textsc{i} data \citep{lab} for
$-72$$<$$v_{LSR}$$<$$+25$ that the best-fit slope for H\,\textsc{i}$<$70 K km/s
is a factor of $\sim$1.9 lower than the best fit slope for 
110 K km/s $<$H\,\textsc{i}$<$70 K km/s, and as a result the implied 
zero-point offsets for \PLANCK~857 GHz differ by $\sim$0.37 MJy/sr.

% CITE KALBERLA LAB PAPER !!!!!

Because of these ambiguities in the relationship between 857 GHz emission
and H\,\textsc{i}, we decided to instead constrain the 857 GHz zero level
by comparison to the FDS99 857 GHz prediction. This renders the 857 GHz 
absolute zero level tied largely to the reliable FIRAS zero point, and to some 
lesser extent to H\,\textsc{i} through the \verb|i100| zero point. 
Specifically, we fit a linear model to the \PLANCK~857 GHz values as a function
of FDS99 predicted 857 GHz. We used a version of the \PLANCK~857 GHz map with 
zodiacal light and point sources removed and smoothed to 1 degree resolution, 
which we will refer to as $\mathcal{I}_{857}$. For this analysis, we considered
$\mathcal{I}_{857}$ to be the independent variable, as it has much higher S/N 
than the FDS99 prediction, henceforward referred to as $\mathcal{F}_{857}$.
We then rebin to $N_{side}$=64 and restrict to pixels with 
$\mathcal{I}_{857}$$<$2.15 MJy/sr. Since \PLANCK~857 GHz smoothed to degree 
resolution has such high S/N, we can safely perform such a cut on 
$\mathcal{I}_{857}$. Figure XX shows the a scatterplot of $\mathcal{I}_{857}$
versus $\mathcal{F}_{857}$, with a moving median and linear fit overplotted.

% mention uniform weights in linear fit, but don't think i want an equation
% for linear fit since it's so simple to begin with

% sentence saying slope is close to unity, and relationship indeed looks linear

% sentence or two explaining split into quadrants, differences in slope
% and offset probably due to zodiacal light and/or issues with FDS T2 map
% say how this quadrants exercise (via rms) allows us to define 857 GHz
% uncertainty

% what HI intensity does the 2.15 MJy/sr 857 GHz correspond to ?
%  ---> pretty high actually

% mention use of bandpass correction factors when doing Planck vs. prediction
% regressions

\subsubsection{Relative Zero Level}

At 353 GHz, 545 GHz, 857 GHz, we have 
adopted the zero-point offsets of \cite{planckdust} Table 1, which were derived
 by correlating \PLANCK~857 GHz versus H\,\textsc{i} at low column density, and
then by correlating the other \PLANCK~channels against the corrected 857 GHz 
map. We have not altered the \verb|i100| zero-point in any way. We have also 
removed the Solar dipole residual according to \cite{planckdust}, by 
subtracting a dipole pattern oriented toward 
$(l, b) = (263.99^{\circ}, 48.26^{\circ})$ and scaled according to their 
Table 1.
